Digital History in Finland, 1488-1828

### 2016-07-13 inst/examples/manuscript-krakow.Rmd
Rmd update

```{r drop1700B, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=7}
catalogue <- "Fennica"
place <- "Turku"

@@

```{r publisherpapertitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
for (catalogue in c("Fennica", "Kungliga")) {

@@

```{r language1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}

@@

```{r topics3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat","hautajaiset","häät","juhlamenot")
catalogue <- "Fennica"
  if (catalogue == "Fennica") {
    df <- df.full # full time span
  } else if (catalogue == "Kungliga") {
    df <- df0 # selected time span
  }
  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)

@@

```{r 201606krakow-turkuvsother, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=10, fig.show="hold", out.width="430px"}
df <- df0 %>%
      filter(catalog == "Fennica") %>% 
      filter(!is.na(country)) %>%
      filter(!is.na(publication_place) & !is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01)

@@

```{r polev1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6, out.width="280px", fig.show="hold"}
sel.places = c("Stockholm", "Uppsala", "Lund", "Greifswald", "Turku")
sel.years = c(1760, 1780)
pics <- list()

>>>>

```{r drop1700BB, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=7}
catalogue <- "Fennica"
place <- "Turku"

@@

```{r publisherpapertitleB, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
for (catalogue in c("Fennica", "Kungliga")) {

@@

```{r language1B, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}

@@

```{r topics3B, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat","hautajaiset","häät","juhlamenot")
catalogue <- "Fennica"
  if (catalogue == "Fennica") {
    df <- df.full # full time span
  } else if (catalogue == "Kungliga") {
    df <- df0 # selected time span
  }
  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)

@@

```{r 201606krakow-turkuvsotherB, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=10, fig.show="hold", out.width="430px"}
df <- df0 %>%
      filter(catalog == "Fennica") %>% 
      filter(!is.na(country)) %>%
      filter(!is.na(publication_place) & !is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01)

@@

```{r polev1b, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6, out.width="280px", fig.show="hold"}
sel.places = c("Stockholm", "Uppsala", "Lund", "Greifswald", "Turku")
sel.years = c(1760, 1780)
pics <- list()
